---
title: "TBC *"
author: "Mikel Diaz-Rodriguez"
date: "March 7th, 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE,
                      echo = TRUE)
```

# Introduction

This document contains code to enable reproducibility of the paper "Living in the mountains. Settlement patterns in Northwestern Iberia during Palaeolithic period".

For this, it is necessary to execute the steps shown in the following lines.

# Complete Spatial Randomness

### Necessary packages

Import the necessary packages to analyse the CSR.

```{r echo=FALSE, results='hide'}
# ipak function: install and load multiple R packages.
# check to see if packages are installed. Install them if they are not, then load them into the R session.

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
# usage
packages <- c("GGally", "readxl", "rgdal", "rgeos", "sp", "spatstat", "tidyverse", "dismo", "MASS", "ggplot2", "plyr", "maps", "maptools", "raster", "geostatsp", "patchwork", "foreach", "purrrlyr")
ipak(packages)
```

### Import data

Import the data used in CSR analysis.

```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
# set your working directory
setwd("~/mountain_ranges/shp")

# add the study areas
area_northern <- readOGR(dsn="area_northern.shp", layer="area_northern")
area_central <- readOGR(dsn="area_central.shp", layer="area_central")

# and check it
plot(area_northern)
plot(area_central)

# add the sites
sites_northern <- readOGR(dsn="sites_northern.shp", layer="sites_northern")
sites_central <- readOGR(dsn="sites_central.shp", layer="sites_central")

# add the random sites
random_sites_northern <- readOGR(dsn="random_sites_northern.shp", layer="random_sites_northern")
random_sites_central <- readOGR(dsn="random_sites_central.shp", layer="random_sites_central")

# plot each study area, sites and the random sites and check if everything looks OK
## check the Northern Mountain range area
plot(area_northern)
plot(sites_northern, col="blue", pch=20, add=T)
plot(random_sites_northern, col="grey", pch=20, add=T)

## check the Central Mountain range area
plot(area_central)
plot(sites_central, col="red", pch=20, add=T)
plot(random_sites_central, col="grey", pch=20, add=T)

# remove any sites with the same grid reference
sites_northern <- remove.duplicates(sites_northern)
sites_central <- remove.duplicates(sites_central)

# select the points inside each study area 
sitesSubN <- sites_northern[area_northern,]
sitesSubC <- sites_central[area_central,]



# check to see that the points have been removed in each area
## Northern Mountain ranges
plot(area_northern)
plot(sitesSubN, col="red", pch=20, add=T)

## Central Mountain ranges
plot(area_central)
plot(sitesSubC, col="red", pch=20, add=T)


# set a window as the Northern area
window1 <- as.owin(area_northern)
plot(window1)

# create a ppp object
sitesSubN.ppp <- ppp(x=sitesSubN$utmx,y=sitesSubN$utmy,window=window1)

# plot the sites and the Northern area
plot(sitesSubN.ppp,pch=16,cex=0.5, main="Northern Mountain range sites")


# set a window as the Central area
window2 <- as.owin(area_central)
plot(window2)

# create a ppp object
sitesSubC.ppp <- ppp(x=sitesSubC$utmx,y=sitesSubC$utmy,window=window2)

# plot the sites and the Northern area
plot(sitesSubC.ppp,pch=16,cex=0.5, main="Central Mountain range sites")
```

### Check the CSR

```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
# CSR Analysis

## Northern Mountain ranges
### Normality test for sites
shapiro.test(sitesSubN$utmx)

### Normality test for random sites
shapiro.test(random_sites_northern$utmx)

### If the alternative hypothesis is accepted, the points do not follow a normal distribution. To verify this, the K-S Test is used.
### K-S is a non-parametric test to check if the points of both samples belong to the same population.
ks.test(sitesSubN$utmx,random_sites_northern$utmx)


## Central Mountain ranges
### Normality test for sites
shapiro.test(sitesSubC$utmx)

### Normality test for random sites
shapiro.test(random_sites_central$utmx)

### K-S Test
ks.test(sitesSubC$utmx,random_sites_central$utmx)
```

### Create Figures 2 and 3

```{r echo=TRUE, results='hide'}
## K, L and G Functions
# set the simulations
sims <- 99
# to get 95% envelope
nrank <- round((sims + 1) / 100 * 2.5, 0)

# K, L and G functions for Northern Mountain ranges
KfunctionN <- envelope(sitesSubN.ppp,Kest, nsim=sims,rank=nrank, correction="best") 
KinhomFunctionN <- envelope(sitesSubN.ppp,Kinhom, nsim=sims,rank=nrank, correction="best")
LFunctionN <- envelope(sitesSubN.ppp,Lest, nsim=sims,rank=nrank, correction="best")
LinhomFunctionN <- envelope(sitesSubN.ppp,Linhom, nsim=sims,rank=nrank, correction="best")
GFunctionN <- envelope(sitesSubN.ppp,Gest, nsim=sims,rank=nrank, correction="best")
GinhomFunctionN <- envelope(sitesSubN.ppp,Ginhom, nsim=sims,rank=nrank, correction="best")

# K, L and G functions for Central Mountain ranges
KfunctionC <- envelope(sitesSubC.ppp,Kest, nsim=sims,rank=nrank, correction="best") 
KinhomFunctionC <- envelope(sitesSubC.ppp,Kinhom, nsim=sims,rank=nrank, correction="best")
LFunctionC <- envelope(sitesSubC.ppp,Lest, nsim=sims,rank=nrank, correction="best")
LinhomFunctionC <- envelope(sitesSubC.ppp,Linhom, nsim=sims,rank=nrank, correction="best")
GFunctionC <- envelope(sitesSubC.ppp,Gest, nsim=sims,rank=nrank, correction="best")
GinhomFunctionC <- envelope(sitesSubC.ppp,Ginhom, nsim=sims,rank=nrank, correction="best")

# create Figure 2
par(mar=c(3, 3, 3, 3), mfrow=c(3,2))
plot(KfunctionN,main="a. K Function for the Northern area (homogeneous)",legend=FALSE)
plot(KinhomFunctionN,main="b. K Function for the Northern area (inhomogeneous)",legend=FALSE)
plot(LFunctionN,main="c. L Function for the Northern area (homogeneous)",legend=FALSE)
plot(LinhomFunctionN,main="d. L Function for the Northern area (inhomogeneous)",legend=FALSE) 
plot(GFunctionN,main="e. G Function for the Northern area (homogeneous)",legend=FALSE) 
plot(GinhomFunctionN,main="f. G Function for the Northern area (inhomogeneous)",legend=FALSE)
par(mfrow=c(1,1))
png(file = "~/output/Figure2.png",width = 900,height = 1200)
dev.off()

# create Figure 3
par(mar=c(3, 3, 3, 3), mfrow=c(3,2))
plot(KfunctionC,main="a. K Function for the Central area (homogeneous)",legend=FALSE)
plot(KinhomFunctionC,main="b. K Function for the Central area (inhomogeneous)",legend=FALSE)
plot(LFunctionC,main="c. L Function for the Central area (homogeneous)",legend=FALSE)
plot(LinhomFunctionC,main="d. L Function for the Central area (inhomogeneous)",legend=FALSE) 
plot(GFunctionC,main="e. G Function for the Central area (homogeneous)",legend=FALSE) 
plot(GinhomFunctionC,main="f. G Function for the Central area (inhomogeneous)",legend=FALSE)
par(mfrow=c(1,1))
png(file = "~/output/Figure3.png",width = 900,height = 1200)
dev.off()
```

# Kernel density plots

Process to create the kernel density plots comparing archaeological sites and 999 randomly resampled background points.

## Northern area

```{r echo=TRUE, results='hide'}
# Northern area

## set your working directory
setwd("~/mountain_ranges/shp")

## add the sites
sites_northern <- readOGR(dsn="sites_northern.shp", layer="sites_northern")


## set the working directory
setwd("~/mountain_ranges/grids")

## Import variables and set the same extent for everyone

ALTA_northern <- raster("ALTA_northern.tif")

TPI100_northern <- raster("TPI100_northern.asc")

TPI500_northern <- raster("TPI500_northern.asc")

TPI1000_northern <- raster("TPI1000_northern.asc")

SLO_northern <- raster("SLO_northern.tif") 

ASP_northern <- raster("ASP_northern.tif") 

HYDROE_northern <- raster("HYDROE_northern.tif")

HYDROC_northern <- raster("HYDROC_northern.tif") 

WET_northern <- raster("WET_northern.tif") 

GEOLE_northern <- raster("GEOLE_northern.tif")

GEOLC_northern <- raster("GEOLC_northern.tif")

VISPR_northern <- raster("VISPR_northern.tif")

LCPC_northern <- raster("LCPC_northern.tif")

TOTINS_northern <- raster("TOTINS_northern.asc") 

DIRINS_northern <- raster("DIRINS_northern.asc") 

DIFINS_northern <- raster("DIFINS_northern.asc")  

WIND_northern <- raster("WIND_northern.asc") 

CPFPCGc_northern <- raster("CPFPCGc_northern.tif")

CPFPCDc_northern <- raster("CPFPCDc_northern.tif")
```

## ALTA

Create kernel density plot graph for the variable ALTA.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`ALTA (m)` <-  
  raster::extract(ALTA_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  ALTA_northern %>%
  density(from = 450, to = 766, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(ALTA = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_ALTA_values <- ALTA_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_ALTA_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_ALTA_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 53, to = 1054, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("ALTA", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_ALTA_densities,
            mapping = aes(x = ALTA,
                          y = Frequency)) +
  geom_ribbon(data = background_ALTA_densities,
              mapping = aes(x = ALTA,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = ALTA ,
                          y = Frequency),
            color = "red") +ggtitle("a. ALTA in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureALTA-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_altitude_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_ALTA_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`ALTA (m)`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_altitude_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_altitude_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_altitude_MWU, 3)
```

## TPI100

Create kernel density plot graph for the variable TPI100.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TPI100` <-  
  raster::extract(TPI100_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TPI100_northern %>%
  density(from = -3, to = 10, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TPI100 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI100_values <- TPI100_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI100_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI100_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = -34, to = 30, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI100", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI100_densities,
            mapping = aes(x = TPI100,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI100_densities,
              mapping = aes(x = TPI100,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TPI100,
                          y = Frequency),
            color = "red") +ggtitle("b. TPI100 in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureTPI100-Northern.png",width = 1000,height = 437)
dev.off()

# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI100_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI100_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TPI100`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI100_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI100_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI100_MWU, 3)
```

## TPI500

Create kernel density plot graph for the variable TPI500.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TPI500` <-  
  raster::extract(TPI500_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TPI500_northern %>%
  density(from = -3, to = 10.5, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TPI500 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI500_values <- TPI500_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI500_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI500_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = -106, to = 114, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI500", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI500_densities,
            mapping = aes(x = TPI500,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI500_densities,
              mapping = aes(x = TPI500,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TPI500,
                          y = Frequency),
            color = "red") +ggtitle("a. TPI500 variable in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureTPI500-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI500_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI500_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TPI500`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI500_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI500_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI500_MWU, 3)
```

## TPI1000

Create kernel density plot graph for the variable TPI1000.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TPI1000` <-  
  raster::extract(TPI1000_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TPI1000_northern %>%
  density(from = -3, to = 10, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TPI1000 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI1000_values <- TPI1000_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI1000_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI1000_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = -163, to = 205, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI1000", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI1000_densities,
            mapping = aes(x = TPI1000,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI1000_densities,
              mapping = aes(x = TPI1000,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TPI1000,
                          y = Frequency),
            color = "red") +ggtitle("b. TPI1000 in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureTPI1000-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI1000_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI1000_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TPI1000`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI1000_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI1000_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI1000_MWU, 3)
```

## SLO

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`SLO` <-  
  raster::extract(SLO_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  SLO_northern %>%
  density(from = 0, to = 26, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(SLO = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_SLO_values <- SLO_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_SLO_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_SLO_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 61, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("SLO", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_SLO_densities,
            mapping = aes(x = SLO,
                          y = Frequency)) +
  geom_ribbon(data = background_SLO_densities,
              mapping = aes(x = SLO,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = SLO,
                          y = Frequency),
            color = "red") +ggtitle("c. SLO in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureSLO-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_SLO_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_SLO_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`SLO`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_SLO_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_SLO_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_SLO_MWU, 3)
```

## ASP

Create kernel density plot graph for the variable ASP.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`ASP` <-  
  raster::extract(ASP_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  ASP_northern %>%
  density(from = 11, to = 331, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(ASP = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_ASP_values <- ASP_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_ASP_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_ASP_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 360, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("ASP", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_ASP_densities,
            mapping = aes(x = ASP,
                          y = Frequency)) +
  geom_ribbon(data = background_ASP_densities,
              mapping = aes(x = ASP,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = ASP,
                          y = Frequency),
            color = "red") +ggtitle("c. ASP in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureASP-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_ASP_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_ASP_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`ASP`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_ASP_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_ASP_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_ASP_MWU, 3)
```

## HYDROE

Create kernel density plot graph for the variable HYDROE.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`HYDROE` <-  
  raster::extract(HYDROE_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())

## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  HYDROE_northern %>%
  density(from = 34, to = 1784, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(HYDROE = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_HYDROE_values <- HYDROE_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_HYDROE_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_HYDROE_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 2834, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("HYDROE", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_HYDROE_densities,
            mapping = aes(x = HYDROE,
                          y = Frequency)) +
  geom_ribbon(data = background_HYDROE_densities,
              mapping = aes(x = HYDROE,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = HYDROE,
                          y = Frequency),
            color = "red") +ggtitle("d. HYDROE in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureHYDROE-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_HYDROE_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_HYDROE_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`HYDROE`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_HYDROE_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_HYDROE_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_HYDROE_MWU, 3)
```

## HYDROC

Create kernel density plot graph for the variable HYDROC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`HYDROC` <-  
  raster::extract(HYDROC_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  HYDROC_northern %>%
  density(from = 3, to = 100, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(HYDROC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_HYDROC_values <- HYDROC_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_HYDROC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_HYDROC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 144, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("HYDROC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_HYDROC_densities,
            mapping = aes(x = HYDROC,
                          y = Frequency)) +
  geom_ribbon(data = background_HYDROC_densities,
              mapping = aes(x = HYDROC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = HYDROC,
                          y = Frequency),
            color = "red") +ggtitle("d. HYDROC in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureHYDROC-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_HYDROC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_HYDROC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`HYDROC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_HYDROC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_HYDROC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_HYDROC_MWU, 3)
```

## WET

Create kernel density plot graph for the variable WET.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WET` <-  
  raster::extract(WET_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WET_northern %>%
  density(from = 0, to = 45, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WET = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WET_values <- WET_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WET_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 113, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WET", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WET_densities,
            mapping = aes(x = WET,
                          y = Frequency)) +
  geom_ribbon(data = background_WET_densities,
              mapping = aes(x = WET,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WET,
                          y = Frequency),
            color = "red") +ggtitle("a. WET in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureWET-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WET_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WET`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WET_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WET_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WET_MWU, 3)
```

## GEOLE

Create kernel density plot graph for the variable GEOLE.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WET` <-  
  raster::extract(WET_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WET_northern %>%
  density(from = 0, to = 45, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WET = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WET_values <- WET_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WET_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 113, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WET", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WET_densities,
            mapping = aes(x = WET,
                          y = Frequency)) +
  geom_ribbon(data = background_WET_densities,
              mapping = aes(x = WET,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WET,
                          y = Frequency),
            color = "red") +ggtitle("a. WET in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureGEOLE-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WET_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WET`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WET_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WET_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WET_MWU, 3)
```

## GEOLC

Create kernel density plot graph for the variable GEOLC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`GEOLC` <-  
  raster::extract(GEOLC_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  GEOLC_northern %>%
  density(from = 0, to = 153, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(GEOLC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_GEOLC_values <- GEOLC_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_GEOLC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_GEOLC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 360, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("GEOLC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_GEOLC_densities,
            mapping = aes(x = GEOLC,
                          y = Frequency)) +
  geom_ribbon(data = background_GEOLC_densities,
              mapping = aes(x = GEOLC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = GEOLC,
                          y = Frequency),
            color = "red") +ggtitle("c. GEOLC in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureGEOLC-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_GEOLC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_GEOLC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`GEOLC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_GEOLC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_GEOLC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_GEOLC_MWU, 3)
```

## VISPR

Create kernel density plot graph for the variable VISPR.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`VISPR` <-  
  raster::extract(VISPR_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  VISPR_northern %>%
  density(from = 0, to = 75, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(VISPR = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_VISPR_values <- VISPR_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_VISPR_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_VISPR_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 153, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("VISPR", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_VISPR_densities,
            mapping = aes(x = VISPR,
                          y = Frequency)) +
  geom_ribbon(data = background_VISPR_densities,
              mapping = aes(x = VISPR,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = VISPR,
                          y = Frequency),
            color = "red") +ggtitle("d. VISPR in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureVISPR-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_VISPR_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_VISPR_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`VISPR`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_VISPR_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_VISPR_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_VISPR_MWU, 3)
```

## LCPC

Create kernel density plot graph for the variable LCPC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`LCPC` <-  
  raster::extract(LCPC_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  LCPC_northern %>%
  density(from = 0, to = 9.95, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(LCPC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_LCPC_values <- LCPC_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_LCPC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_LCPC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 142, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("LCPC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_LCPC_densities,
            mapping = aes(x = LCPC,
                          y = Frequency)) +
  geom_ribbon(data = background_LCPC_densities,
              mapping = aes(x = LCPC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = LCPC,
                          y = Frequency),
            color = "red") +ggtitle("a. LCPC in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureLCPC-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_LCPC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_LCPC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`LCPC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_LCPC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_LCPC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_LCPC_MWU, 3)
```

## TOTINS

Create kernel density plot graph for the variable TOTINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TOTINS` <-  
  raster::extract(TOTINS_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TOTINS_northern %>%
  density(from = 3.5, to = 5.2, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TOTINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TOTINS_values <- TOTINS_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TOTINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TOTINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0.7, to = 6.37, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TOTINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TOTINS_densities,
            mapping = aes(x = TOTINS,
                          y = Frequency)) +
  geom_ribbon(data = background_TOTINS_densities,
              mapping = aes(x = TOTINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TOTINS,
                          y = Frequency),
            color = "red") +ggtitle("a. TOTINS in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureTOTINS-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TOTINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TOTINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TOTINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TOTINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TOTINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TOTINS_MWU, 3)
```

## DIRINS

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`DIRINS` <-  
  raster::extract(DIRINS_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  DIRINS_northern %>%
  density(from = 2.6, to = 4.5, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(DIRINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_DIRINS_values <- DIRINS_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_DIRINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_DIRINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 5.6, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("DIRINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_DIRINS_densities,
            mapping = aes(x = DIRINS,
                          y = Frequency)) +
  geom_ribbon(data = background_DIRINS_densities,
              mapping = aes(x = DIRINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = DIRINS,
                          y = Frequency),
            color = "red") +ggtitle("b. DIRINS in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureDIRINS-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_DIRINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_DIRINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`DIRINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_DIRINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_DIRINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_DIRINS_MWU, 3)
```

## DIFINS

Create kernel density plot graph for the variable DIFINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`DIFINS` <-  
  raster::extract(DIFINS_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  DIFINS_northern %>%
  density(from = 0.8, to = 0.93, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(DIFINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_DIFINS_values <- DIFINS_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_DIFINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_DIFINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0.69, to = 0.98, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("DIFINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_DIFINS_densities,
            mapping = aes(x = DIFINS,
                          y = Frequency)) +
  geom_ribbon(data = background_DIFINS_densities,
              mapping = aes(x = DIFINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = DIFINS,
                          y = Frequency),
            color = "red") +ggtitle("c. DIFINS in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureDIFINS-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_DIFINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_DIFINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`DIFINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_DIFINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_DIFINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_DIFINS_MWU, 3)
```

## WIND

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WIND` <-  
  raster::extract(WIND_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WIND_northern %>%
  density(from = 0.7, to = 1.24, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WIND = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WIND_values <- WIND_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WIND_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WIND_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0.74, to = 1.34, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WIND", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WIND_densities,
            mapping = aes(x = WIND,
                          y = Frequency)) +
  geom_ribbon(data = background_WIND_densities,
              mapping = aes(x = WIND,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WIND,
                          y = Frequency),
            color = "red") +ggtitle("b. WIND variable in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureWIND-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WIND_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WIND_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WIND`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WIND_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WIND_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WIND_MWU, 3)
```

## CPFPCGc

Create kernel density plot graph for the variable CPFPCGc.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`CPFPCGc` <-  
  raster::extract(CPFPCGc_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  CPFPCGc_northern %>%
  density(from = 4, to = 432, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(CPFPCGc = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_CPFPCGc_values <- CPFPCGc_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_CPFPCGc_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_CPFPCGc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 673, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("CPFPCGc", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_CPFPCGc_densities,
            mapping = aes(x = CPFPCGc,
                          y = Frequency)) +
  geom_ribbon(data = background_CPFPCGc_densities,
              mapping = aes(x = CPFPCGc,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = CPFPCGc ,
                          y = Frequency),
            color = "red") +ggtitle("c. CPFPCGc in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureCPFPCGc-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_CPFPCGc_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_CPFPCGc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`CPFPCGc`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_CPFPCGc_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_CPFPCGc_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_CPFPCGc_MWU, 3)
```

## CPFPCDc

Create kernel density plot graph for the variable CPFPCDc.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`CPFPCDc` <-  
  raster::extract(CPFPCDc_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  CPFPCDc_northern %>%
  density(from = 0, to = 0, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(CPFPCDc = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_CPFPCDc_values <- CPFPCDc_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_CPFPCDc_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_CPFPCDc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 8.7, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("CPFPCDc", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_CPFPCDc_densities,
            mapping = aes(x = CPFPCDc,
                          y = Frequency)) +
  geom_ribbon(data = background_CPFPCDc_densities,
              mapping = aes(x = CPFPCDc,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = CPFPCDc ,
                          y = Frequency),
            color = "red") +ggtitle("d. CPFPCDc in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureCPFPCDc-Northern.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_CPFPCDc_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_CPFPCDc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`CPFPCGc`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_CPFPCDc_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_CPFPCDc_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_CPFPCDc_MWU, 3)
```

## Central area

```{r echo=TRUE, results='hide'}
# Central area

## set your working directory
setwd("~/mountain_ranges/shp")

## add the sites
sites_central <- readOGR(dsn="sites_central.shp", layer="sites_central")


## set the working directory
setwd("~/mountain_ranges/grids")

## Import variables and set the same extent for everyone
ALTA_central <- raster("ALTA_central.tif")

TPI100_central <- raster("TPI100_central.asc")

TPI500_central <- raster("TPI500_central.asc")

TPI1000_central <- raster("TPI1000_central.asc")

SLO_central <- raster("SLO_central.tif") 

ASP_central <- raster("ASP_central.tif") 

HYDROE_central <- raster("HYDROE_central.tif")

HYDROC_central <- raster("HYDROC_central.tif") 

WET_central <- raster("WET_central.tif") 

GEOLE_central <- raster("GEOLE_central.tif")

GEOLC_central <- raster("GEOLC_central.tif")

VISPR_central <- raster("VISPR_central.tif")

LCPC_central <- raster("LCPC_central.tif")

TOTINS_central <- raster("TOTINS_central.asc") 

DIRINS_central <- raster("DIRINS_central.asc") 

DIFINS_central <- raster("DIFINS_central.asc")  

WIND_central <- raster("WIND_central.asc") 

CPFPCDc_central <- raster("CPFPCDc_central.tif")

CPFPCGc_central <- raster("CPFPCGc_central.tif")
```

## ALTA

Create kernel density plot graph for the variable ALTA.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`ALTA (m)` <-  
  raster::extract(ALTA_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  ALTA_central %>%
  density(from = 471, to = 759, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(ALTA = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_ALTA_values <- ALTA_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_ALTA_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_ALTA_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 245, to = 834, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("ALTA", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_ALTA_densities,
            mapping = aes(x = ALTA,
                          y = Frequency)) +
  geom_ribbon(data = background_ALTA_densities,
              mapping = aes(x = ALTA,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = ALTA,
                          y = Frequency),
            color = "red") +ggtitle("a. ALTA in Central Mountain ranges")

# Export the figure
png(file = "~/output/FigureALTA-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_ALTA_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_ALTA_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`ALTA (m)`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_ALTA_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_ALTA_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_ALTA_MWU, 3)
```

## TPI100

Create kernel density plot graph for the variable TPI100.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`TPI100` <-  
  raster::extract(TPI100_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  TPI100_central %>%
  density(from = -19.6531, to = 19.1837, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(TPI100 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI100_values <- TPI100_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI100_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI100_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = -19.6531, to = 19.1837, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI100", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI100_densities,
            mapping = aes(x = TPI100,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI100_densities,
              mapping = aes(x = TPI100,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = TPI100,
                          y = Frequency),
            color = "red") +ggtitle("b. TPI100 in Central Mountain ranges")

# Export the figure
png(file = "~/output/FigureTPI100-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI100_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI100_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`TPI100`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI100_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI100_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI100_MWU, 3)
```

## TPI500

Create kernel density plot graph for the variable TPI500.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`TPI500` <-  
  raster::extract(TPI500_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  TPI500_central %>%
  density(from = -60.73590, to = 62.37790, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(TPI500 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI500_values <- TPI500_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI500_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI500_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = -60.73590, to = 62.37790, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI500", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI500_densities,
            mapping = aes(x = TPI500,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI500_densities,
              mapping = aes(x = TPI500,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = TPI500,
                          y = Frequency),
            color = "red") +ggtitle("c. TPI500 in Central Mountain ranges")

# Export the figure
png(file = "~/output/FigureTPI500-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI500_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI500_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`TPI500`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI500_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI500_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI500_MWU, 3)
```

## TPI1000

Create kernel density plot graph for the variable TPI100.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`TPI1000` <-  
  raster::extract(TPI1000_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  TPI1000_central %>%
  density(from = -90.0561, to = 109.978, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(TPI1000 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI1000_values <- TPI1000_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI1000_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI1000_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = -90.0561, to = 109.978, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI1000", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI1000_densities,
            mapping = aes(x = TPI1000,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI1000_densities,
              mapping = aes(x = TPI1000,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = TPI1000,
                          y = Frequency),
            color = "red") +ggtitle("d. TPI1000 in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureTPI1000-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI1000_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI1000_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`TPI1000`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI1000_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI1000_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI1000_MWU, 3)
```

## SLO

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`SLO` <-  
  raster::extract(SLO_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  SLO_central %>%
  density(from = 0, to = 16, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(SLO = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_SLO_values <- SLO_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_SLO_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_SLO_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 40, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("SLO", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_SLO_densities,
            mapping = aes(x = SLO,
                          y = Frequency)) +
  geom_ribbon(data = background_SLO_densities,
              mapping = aes(x = SLO,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = SLO,
                          y = Frequency),
            color = "red") +ggtitle("a. SLO in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureSLO-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_SLO_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_SLO_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`SLO`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_SLO_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_SLO_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_SLO_MWU, 3)
```

## ASP

Create kernel density plot graph for the variable ASP.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`ASP` <-  
  raster::extract(ASP_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  ASP_central %>%
  density(from = 11, to = 347, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(ASP = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_ASP_values <- ASP_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_ASP_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_ASP_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 360, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("ASP", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_ASP_densities,
            mapping = aes(x = ASP,
                          y = Frequency)) +
  geom_ribbon(data = background_ASP_densities,
              mapping = aes(x = ASP,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = ASP,
                          y = Frequency),
            color = "red") +ggtitle("b. ASP variable in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureASP-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_ASP_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_ASP_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`ASP`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_ASP_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_ASP_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_ASP_MWU, 3)
```

## HYDROE

Create kernel density plot graph for the variable HYDROE.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`HYDROE` <-  
  raster::extract(HYDROE_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  HYDROE_central %>%
  density(from = 33, to = 2019, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(HYDROE = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_HYDROE_values <- HYDROE_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_HYDROE_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_HYDROE_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 2586, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("HYDROE", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_HYDROE_densities,
            mapping = aes(x = HYDROE,
                          y = Frequency)) +
  geom_ribbon(data = background_HYDROE_densities,
              mapping = aes(x = HYDROE,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = HYDROE,
                          y = Frequency),
            color = "red") +ggtitle("a. HYDROE in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureHYDROE-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_HYDROE_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_HYDROE_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`HYDROE`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_HYDROE_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_HYDROE_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_HYDROE_MWU, 3)
```

## HYDROC

Create kernel density plot graph for the variable HYDROC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`HYDROC` <-  
  raster::extract(HYDROC_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  HYDROC_central %>%
  density(from = 5, to = 108, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(HYDROC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_HYDROC_values <- HYDROC_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_HYDROC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_HYDROC_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 141, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("HYDROC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_HYDROC_densities,
            mapping = aes(x = HYDROC,
                          y = Frequency)) +
  geom_ribbon(data = background_HYDROC_densities,
              mapping = aes(x = HYDROC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = HYDROC,
                          y = Frequency),
            color = "red") +ggtitle("b. HYDROC in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureHYDROC-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_HYDROC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_HYDROC_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`HYDROC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_HYDROC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_HYDROC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_HYDROC_MWU, 3)
```

## WET

Create kernel density plot graph for the variable WET.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WET` <-  
  raster::extract(WET_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WET_northern %>%
  density(from = 0, to = 45, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WET = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WET_values <- WET_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WET_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 113, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WET", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WET_densities,
            mapping = aes(x = WET,
                          y = Frequency)) +
  geom_ribbon(data = background_WET_densities,
              mapping = aes(x = WET,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WET,
                          y = Frequency),
            color = "red") +ggtitle("a. WET in Northern Mountain ranges")

# Export the figure
png(file = "~/output/FigureWET-Central.png",width = 1000,height = 437)
dev.off()



# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WET_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WET`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WET_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WET_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WET_MWU, 3)
```

## GEOLE

Create kernel density plot graph for the variable GEOLE.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`GEOLE` <-  
  raster::extract(GEOLE_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  GEOLE_central %>%
  density(from = 5366, to = 9523, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(GEOLE = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_GEOLE_values <- GEOLE_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_GEOLE_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_GEOLE_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 19671, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("GEOLE", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_GEOLE_densities,
            mapping = aes(x = GEOLE,
                          y = Frequency)) +
  geom_ribbon(data = background_GEOLE_densities,
              mapping = aes(x = GEOLE,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = GEOLE,
                          y = Frequency),
            color = "red") +ggtitle("d. GEOLE in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureGEOLE-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_GEOLE_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_GEOLE_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`GEOLE`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_GEOLE_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_GEOLE_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_GEOLE_MWU, 3)
```

## GEOLC

Create kernel density plot graph for the variable GEOLC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`GEOLC` <-  
  raster::extract(GEOLC_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  GEOLC_central %>%
  density(from = 259, to = 475, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(GEOLC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_GEOLC_values <- GEOLC_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_GEOLC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_GEOLC_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 956, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("GEOLC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_GEOLC_densities,
            mapping = aes(x = GEOLC,
                          y = Frequency)) +
  geom_ribbon(data = background_GEOLC_densities,
              mapping = aes(x = GEOLC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = GEOLC,
                          y = Frequency),
            color = "red") +ggtitle("a. GEOLC in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureGEOLC-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_GEOLC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_GEOLC_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`GEOLC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_GEOLC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_GEOLC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_GEOLC_MWU, 3)
```

## VISPR

Create kernel density plot graph for the variable VISPR.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`VISPR` <-  
  raster::extract(VISPR_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  VISPR_central %>%
  density(from = 0, to = 68, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(VISPR = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_VISPR_values <- VISPR_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_VISPR_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_VISPR_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 156, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("VISPR", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_VISPR_densities,
            mapping = aes(x = VISPR,
                          y = Frequency)) +
  geom_ribbon(data = background_VISPR_densities,
              mapping = aes(x = VISPR,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = VISPR,
                          y = Frequency),
            color = "red") +ggtitle("b. VISPR in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureVISPR-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_VISPR_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_VISPR_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`VISPR`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_VISPR_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_VISPR_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_VISPR_MWU, 3)
```

## LCPC

Create kernel density plot graph for the variable LCPC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`LCPC` <-  
  raster::extract(LCPC_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  LCPC_central %>%
  density(from = 0, to = 14, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(LCPC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_LCPC_values <- LCPC_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_LCPC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_LCPC_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 101, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("LCPC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_LCPC_densities,
            mapping = aes(x = LCPC,
                          y = Frequency)) +
  geom_ribbon(data = background_LCPC_densities,
              mapping = aes(x = LCPC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = LCPC,
                          y = Frequency),
            color = "red") +ggtitle("c. LCPC in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureLCPC-Central.png",width = 1000,height = 437)
dev.off()



# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_LCPC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_LCPC_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`LCPC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_LCPC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_LCPC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_LCPC_MWU, 3)
```

## TOTINS

Create kernel density plot graph for the variable TOTINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`TOTINS` <-  
  raster::extract(TOTINS_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  TOTINS_central %>%
  density(from = 3, to = 6, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(TOTINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TOTINS_values <- TOTINS_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TOTINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TOTINS_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0.6, to = 6.2, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TOTINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TOTINS_densities,
            mapping = aes(x = TOTINS,
                          y = Frequency)) +
  geom_ribbon(data = background_TOTINS_densities,
              mapping = aes(x = TOTINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = TOTINS,
                          y = Frequency),
            color = "red") +ggtitle("c. TOTINS in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureTOTINS-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TOTINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TOTINS_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`TOTINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TOTINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TOTINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TOTINS_MWU, 3)
```

## DIRINS

Create kernel density plot graph for the variable DIRINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`DIRINS` <-  
  raster::extract(DIRINS_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  DIRINS_central %>%
  density(from = 2, to = 5, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(DIRINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_DIRINS_values <- DIRINS_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_DIRINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_DIRINS_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 5.5, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("DIRINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_DIRINS_densities,
            mapping = aes(x = DIRINS,
                          y = Frequency)) +
  geom_ribbon(data = background_DIRINS_densities,
              mapping = aes(x = DIRINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = DIRINS,
                          y = Frequency),
            color = "red") +ggtitle("d. DIRINS in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureDIRINS-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_DIRINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_DIRINS_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`DIRINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_DIRINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_DIRINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_DIRINS_MWU, 3)
```

## DIFINS

Create kernel density plot graph for the variable DIFINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`DIFINS` <-  
  raster::extract(DIFINS_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  DIFINS_central %>%
  density(from = 0.88, to = 0.93, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(DIFINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_DIFINS_values <- DIFINS_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_DIFINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_DIFINS_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0.75, to = 0.93, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("DIFINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_DIFINS_densities,
            mapping = aes(x = DIFINS,
                          y = Frequency)) +
  geom_ribbon(data = background_DIFINS_densities,
              mapping = aes(x = DIFINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = DIFINS,
                          y = Frequency),
            color = "red") +ggtitle("a. DIFINS variable in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureDIFINS-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_DIFINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_DIFINS_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`DIFINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_DIFINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_DIFINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_DIFINS_MWU, 3)
```

## WIND

Create kernel density plot graph for the variable WIND.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`WIND` <-  
  raster::extract(WIND_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  WIND_central %>%
  density(from = 0.79, to = 1.32, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(WIND = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WIND_values <- WIND_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WIND_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WIND_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0.76, to = 1.33, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WIND", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WIND_densities,
            mapping = aes(x = WIND,
                          y = Frequency)) +
  geom_ribbon(data = background_WIND_densities,
              mapping = aes(x = WIND,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = WIND,
                          y = Frequency),
            color = "red") +ggtitle("d. WIND in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureWIND-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WIND_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WIND_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`WIND`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WIND_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WIND_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WIND_MWU, 3)
```

## CPFPCGc

Create kernel density plot graph for the variable CPFPCGc.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`CPFPCGc` <-  
  raster::extract(CPFPCGc_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  CPFPCGc_central %>%
  density(from = 21, to = 197, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(CPFPCGc = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_CPFPCGc_values <- CPFPCGc_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_CPFPCGc_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_CPFPCGc_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 542, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("CPFPCGc", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_CPFPCGc_densities,
            mapping = aes(x = CPFPCGc,
                          y = Frequency)) +
  geom_ribbon(data = background_CPFPCGc_densities,
              mapping = aes(x = CPFPCGc,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = CPFPCGc ,
                          y = Frequency),
            color = "red") +ggtitle("c. CPFPCGc in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureCPFPCGc-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_CPFPCGc_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_CPFPCGc_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`CPFPCGc`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_CPFPCGc_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_CPFPCGc_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_CPFPCGc_MWU, 3)
```

## CPFPCDc

Create kernel density plot graph for the variable CPFPCDc.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Central area
sites_central_spdf <- SpatialPointsDataFrame(sites_central, data.frame(sites_central))


sites_central$`CPFPCDc` <-  
  raster::extract(CPFPCDc_central, 
                  sites_central_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_central_densities <- sites_central %$%
  CPFPCDc_central %>%
  density(from = 0, to = 0, n = 61) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 61) %>%
  dplyr::rename(CPFPCDc = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_CPFPCDc_values <- CPFPCDc_central %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_CPFPCDc_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_CPFPCDc_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    density(from = 0, to = 3.7, n = 61) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 61)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("CPFPCDc", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_CPFPCDc_densities,
            mapping = aes(x = CPFPCDc,
                          y = Frequency)) +
  geom_ribbon(data = background_CPFPCDc_densities,
              mapping = aes(x = CPFPCDc,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_central_densities,
            mapping = aes(x = CPFPCDc ,
                          y = Frequency),
            color = "red") +ggtitle("b. CPFPCDc in Central Mountain ranges")


# Export the figure
png(file = "~/output/FigureCPFPCDc-Central.png",width = 1000,height = 437)
dev.off()


# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_CPFPCDc_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_CPFPCDc_values %>%
    sample(nrow(sites_central),
           replace = FALSE) %>%
    wilcox.test(x = sites_central$`CPFPCDc`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_CPFPCDc_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_CPFPCDc_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_CPFPCDc_MWU, 3)
```

# Boxplots

Process to create the boxplots comparing archaeological sites and random points.

## Northern area

```{r echo=TRUE, results='hide'}
#Boxplot
## set the working directory
setwd("C:/Users/Mikel/Documents/Curso_2022-2023/Sierras_paper/Github/mountain_ranges/csv")

## Import files
boxplot_variables_northern <- read.csv(file = "C:/Users/Mikel/Documents/Curso_2022-2023/Sierras_paper/Github/mountain_ranges/csv/boxplot_variables_northern.csv",header=TRUE, sep=";", stringsAsFactors=F, dec=",")
boxplot_variables_central <- read.csv(file = "C:/Users/Mikel/Documents/Curso_2022-2023/Sierras_paper/Github/mountain_ranges/csv/boxplot_variables_central.csv",header=TRUE, sep=";", stringsAsFactors=F, dec=",")


## Sites vs random sites in Northern Mountain ranges
## Change the order in x axis
levels(boxplot_variables_northern$Type)
boxplot_variables_northern$Type = factor(boxplot_variables_northern$Type, levels=c("Sites", "Random sites"))
levels(boxplot_variables_northern$Type)

## Delete the grey theme
theme_set(theme_bw())

## Create the ALTm boxplot
p <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=ALTm, fill=Type ))+geom_jitter(aes(x=Type, y=ALTm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ALTm (m.a.s.l.)")+xlab("Type")+ggtitle("a. ALTm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")

## Create the TPI100m boxplot
p1 <- ggplot(data = boxplot_variables_northern, col=c(123,234))+geom_boxplot(aes(x=Type, y=TPI100m, fill=Type ))+geom_jitter(aes(x=Type, y=TPI100m,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI100m")+xlab("Type")+ggtitle("b. TPI100m in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI500m boxplot
p2 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=TPI500m, fill=Type ))+geom_jitter(aes(x=Type, y=TPI500m,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI500m")+xlab("Type")+ggtitle("c. TPI500m in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI500m boxplot
p3 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=TPI1000m, fill=Type ))+geom_jitter(aes(x=Type, y=TPI500m,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI1000m")+xlab("Type")+ggtitle("d. TPI1000m in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOm boxplot
p4 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=SLOm, fill=Type ))+geom_jitter(aes(x=Type, y=SLOm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOm (degrees)")+xlab("Type")+ggtitle("e. SLOm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the ASPm boxplot
p5 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=ASPm, fill=Type ))+geom_jitter(aes(x=Type, y=ASPm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ASPm")+xlab("Type")+ggtitle("f. ASPm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROEm boxplot
p6 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=HYDROEm, fill=Type ))+geom_jitter(aes(x=Type, y=HYDROEm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROEm (m.)")+xlab("Type")+ggtitle("g. HYDROEm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROCm boxplot
p7 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=HYDROCm, fill=Type ))+geom_jitter(aes(x=Type, y=HYDROCm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROCm (minutes)")+xlab("Type")+ggtitle("h. HYDROCm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WETm boxplot
p8 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=WETm, fill=Type ))+geom_jitter(aes(x=Type, y=WETm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WETm (minutes)")+xlab("Type")+ggtitle("i. WETm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none") 

## Create the GEOLEm boxplot
p9 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=GEOLEm, fill=Type ))+geom_jitter(aes(x=Type, y=GEOLEm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLEm (m.)")+xlab("Type")+ggtitle("a. GEOLEm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")

## Create the GEOLCm boxplot
p10 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=GEOLCm, fill=Type ))+geom_jitter(aes(x=Type, y=GEOLCm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLCm (minutes)")+xlab("Type")+ggtitle("b. GEOLCm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the VISPRm boxplot
p11 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=VISPRm, fill=Type ))+geom_jitter(aes(x=Type, y=VISPRm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("VISPRm")+xlab("Type")+ggtitle("c. VISPRm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none") 

## Create the LCPCm boxplot
p12 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=LCPCm, fill=Type ))+geom_jitter(aes(x=Type, y=LCPCm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("LCPCm (minutes)")+xlab("Type")+ggtitle("d. LCPCm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none") 

## Create the TOTINSm boxplot
p13 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=TOTINSm, fill=Type ))+geom_jitter(aes(x=Type, y=TOTINSm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TOTINSm")+xlab("Type")+ggtitle("e. TOTINSm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")

## Create the DIRINSm boxplot
p14 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=DIRINSm, fill=Type ))+geom_jitter(aes(x=Type, y=DIRINSm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIRINSm")+xlab("Type")+ggtitle("f. DIRINSm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")

## Create the DIFINSm boxplot
p15 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=DIFINSm, fill=Type ))+geom_jitter(aes(x=Type, y=DIFINSm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIFINSm")+xlab("Type")+ggtitle("g. DIFINSm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WINDm boxplot
p16 <- ggplot(data = boxplot_variables_northern,col=c(123,234))+geom_boxplot(aes(x=Type, y=WINDm, fill=Type ))+geom_jitter(aes(x=Type, y=WINDm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WINDm")+xlab("Type")+ggtitle("h. WINDm in Northern Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  
```

## Create Figures 7 and 8

```{r echo=TRUE, results='hide'}
## create Figure 7
(p | p1 | p2) /
(p3 | p4 | p5) /
(p6 | p7 | p8)

png(file = "~/output/Figure7.png",width = 1506,height = 750)


## create Figure 8

(p9 | p10 | p11) /
(p12 | p13 | p14)/
(p15 | p16 | guide_area())

png(file = "~/output/Figure8.png",width = 1506,height = 750)
```

## Central area

```{r echo=TRUE, results='hide'}
## Sites vs random sites in Central Mountain ranges
## Change the order in x axis
levels(boxplot_variables_central$Type)
boxplot_variables_central$Type = factor(boxplot_variables_central$Type, levels=c("Sites", "Random sites"))
levels(boxplot_variables_central$Type)

## Delete the grey theme
theme_set(theme_bw())

## Create the ALTm boxplot
p <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=ALTm, fill=Type ))+geom_jitter(aes(x=Type, y=ALTm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ALTm (m.a.s.l.)")+xlab("Type")+ggtitle("a. ALTm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")

## Create the TPI100m boxplot
p1 <- ggplot(data = boxplot_variables_central, col=c(123,234))+geom_boxplot(aes(x=Type, y=TPI100m, fill=Type ))+geom_jitter(aes(x=Type, y=TPI100m,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI100m")+xlab("Type")+ggtitle("b. TPI100m in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI500m boxplot
p2 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=TPI500m, fill=Type ))+geom_jitter(aes(x=Type, y=TPI500m,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI500m")+xlab("Type")+ggtitle("c. TPI500m in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI500m boxplot
p3 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=TPI1000m, fill=Type ))+geom_jitter(aes(x=Type, y=TPI500m,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI1000m")+xlab("Type")+ggtitle("d. TPI1000m in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOm boxplot
p4 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=SLOm, fill=Type ))+geom_jitter(aes(x=Type, y=SLOm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOm (degrees)")+xlab("Type")+ggtitle("e. SLOm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the ASPm boxplot
p5 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=ASPm, fill=Type ))+geom_jitter(aes(x=Type, y=ASPm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ASPm")+xlab("Type")+ggtitle("f. ASPm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROEm boxplot
p6 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=HYDROEm, fill=Type ))+geom_jitter(aes(x=Type, y=HYDROEm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROEm (m.)")+xlab("Type")+ggtitle("g. HYDROEm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROCm boxplot
p7 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=HYDROCm, fill=Type ))+geom_jitter(aes(x=Type, y=HYDROCm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROCm (minutes)")+xlab("Type")+ggtitle("h. HYDROCm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WETm boxplot
p8 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=WETm, fill=Type ))+geom_jitter(aes(x=Type, y=WETm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WETm (minutes)")+xlab("Type")+ggtitle("i. WETm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLEm boxplot
p9 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=GEOLEm, fill=Type ))+geom_jitter(aes(x=Type, y=GEOLEm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLEm (m.)")+xlab("Type")+ggtitle("a. GEOLEm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLCm boxplot
p10 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=GEOLCm, fill=Type ))+geom_jitter(aes(x=Type, y=GEOLCm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLCm (minutes)")+xlab("Type")+ggtitle("b. GEOLCm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the VISPRm boxplot
p11 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=VISPRm, fill=Type ))+geom_jitter(aes(x=Type, y=VISPRm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("VISPRm")+xlab("Type")+ggtitle("c. VISPRm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the LCPCm boxplot
p12 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=LCPCm, fill=Type ))+geom_jitter(aes(x=Type, y=LCPCm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("LCPCm (minutes)")+xlab("Type")+ggtitle("d. LCPCm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TOTINSm boxplot
p13 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=TOTINSm, fill=Type ))+geom_jitter(aes(x=Type, y=TOTINSm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TOTINSm")+xlab("Type")+ggtitle("e. TOTINSm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the DIRINSm boxplot
p14 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=DIRINSm, fill=Type ))+geom_jitter(aes(x=Type, y=DIRINSm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIRINSm")+xlab("Type")+ggtitle("f. DIRINSm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the DIFINSm boxplot
p15 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=DIFINSm, fill=Type ))+geom_jitter(aes(x=Type, y=DIFINSm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIFINSm")+xlab("Type")+ggtitle("g. DIFINSm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WINDm boxplot
p16 <- ggplot(data = boxplot_variables_central,col=c(123,234))+geom_boxplot(aes(x=Type, y=WINDm, fill=Type ))+geom_jitter(aes(x=Type, y=WINDm,fill=Type),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WINDm")+xlab("Type")+ggtitle("h. WINDm in Central Mountain ranges")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  
```

## Create Figures 12 and 13

```{r echo=TRUE, results='hide'}

## create Figure 12
(p | p1 | p2) /
(p3 | p4 | p5) /
(p6 | p7 | p8)

png(file = "~/output/Figure12.png",width = 1506,height = 750)

## create Figure 13
(p9 | p10 | p11) /
(p12 | p13 | p14)/
(p15 | p16 | guide_area())

png(file = "~/output/Figure13.png",width = 1506,height = 750)
```

## Northern Mountain ranges sites vs Central Mountain ranges sites

```{r echo=TRUE, results='hide'}
## Import files
boxplot_northern_vs_central <- read.csv(file = "C:/Users/Mikel/Documents/Curso_2022-2023/Sierras_paper/Github/mountain_ranges/csv/boxplot_northern_vs_central.csv",header=TRUE, sep=";", stringsAsFactors=F, dec=",")

## Delete the grey theme
theme_set(theme_bw())

## Create the ALTA boxplot
p <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=ALTA, fill=Area ))+geom_jitter(aes(x=Area, y=ALTA,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ALTA (m.a.s.l.)")+xlab("Area")+ggtitle("a. ALTA for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the ALTm boxplot
p1 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=ALTm, fill=Area ))+geom_jitter(aes(x=Area, y=ALTm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ALTm (m.a.s.l.)")+xlab("Area")+ggtitle("b. ALTm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")

## Create the TPI100 boxplot
p2 <- ggplot(data = boxplot_northern_vs_central, col=c(123,234))+geom_boxplot(aes(x=Area, y=TPI100, fill=Area ))+geom_jitter(aes(x=Area, y=TPI100,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI100")+xlab("Area")+ggtitle("c. TPI100 for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI100m boxplot
p3 <- ggplot(data = boxplot_northern_vs_central, col=c(123,234))+geom_boxplot(aes(x=Area, y=TPI100m, fill=Area ))+geom_jitter(aes(x=Area, y=TPI100m,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI100m")+xlab("Area")+ggtitle("d. TPI100m for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI500 boxplot
p4 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=TPI500, fill=Area ))+geom_jitter(aes(x=Area, y=TPI500,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI500")+xlab("Area")+ggtitle("e. TPI500 for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI500m boxplot
p5 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=TPI500m, fill=Area ))+geom_jitter(aes(x=Area, y=TPI500m,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI500m")+xlab("Area")+ggtitle("f. TPI500m for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI1000 boxplot
p6 <- ggplot(data = boxplot_northern_vs_central, col=c(123,234))+geom_boxplot(aes(x=Area, y=TPI1000, fill=Area ))+geom_jitter(aes(x=Area, y=TPI1000,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI1000")+xlab("Area")+ggtitle("g. TPI1000 for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TPI1000m boxplot
p7 <- ggplot(data = boxplot_northern_vs_central, col=c(123,234))+geom_boxplot(aes(x=Area, y=TPI1000m, fill=Area ))+geom_jitter(aes(x=Area, y=TPI1000m,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TPI1000m")+xlab("Area")+ggtitle("h. TPI1000m for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the ALTrA boxplot
p8 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=ALTrA, fill=Area ))+geom_jitter(aes(x=Area, y=ALTrA,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ALTrA")+xlab("Area")+ggtitle("a. ALTrA for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the ALTrB boxplot
p9 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=ALTrB, fill=Area ))+geom_jitter(aes(x=Area, y=ALTrB,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ALTrB")+xlab("Area")+ggtitle("b. ALTrB for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLO boxplot
p10 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=SLO, fill=Area ))+geom_jitter(aes(x=Area, y=SLO,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLO")+xlab("Area")+ggtitle("i. SLO for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOm boxplot
p11 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=SLOm, fill=Area ))+geom_jitter(aes(x=Area, y=SLOm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOm")+xlab("Area")+ggtitle("a. SLOm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOga boxplot
p12 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=SLOga, fill=Area ))+geom_jitter(aes(x=Area, y=SLOga,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOga")+xlab("Area")+ggtitle("c. SLOga for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOt boxplot
p13 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=SLOt, fill=Area ))+geom_jitter(aes(x=Area, y=SLOt,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOt")+xlab("Area")+ggtitle("d. SLOt for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOst boxplot
p14 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=SLOst, fill=Area ))+geom_jitter(aes(x=Area, y=SLOst,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOst")+xlab("Area")+ggtitle("e. SLOst for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the SLOpi boxplot
p15 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=SLOpi, fill=Area ))+geom_jitter(aes(x=Area, y=SLOpi,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("SLOpi")+xlab("Area")+ggtitle("f. SLOpi for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the INCr15-45 boxplot
p16 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=INCr45.15, fill=Area ))+geom_jitter(aes(x=Area, y=INCr45.15,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("INCr15-45")+xlab("Area")+ggtitle("g. INCr15-45 for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")   

## Create the ASP boxplot
p17 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=ASP, fill=Area ))+geom_jitter(aes(x=Area, y=ASP,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ASP")+xlab("Area")+ggtitle("b. ASP for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the ASPm boxplot
p18 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=ASPm, fill=Area ))+geom_jitter(aes(x=Area, y=ASPm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("ASPm")+xlab("Area")+ggtitle("c. ASPm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROE boxplot
p19 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=HYDROE, fill=Area ))+geom_jitter(aes(x=Area, y=HYDROE,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROE (m.)")+xlab("Area")+ggtitle("d. HYDROE for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROEm boxplot
p20 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=HYDROEm, fill=Area ))+geom_jitter(aes(x=Area, y=HYDROEm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROEm (m.)")+xlab("Area")+ggtitle("e. HYDROEm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROC boxplot
p21 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=HYDROC, fill=Area ))+geom_jitter(aes(x=Area, y=HYDROC,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROC (minutes)")+xlab("Area")+ggtitle("f. HYDROC for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROCm boxplot
p22 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=HYDROCm, fill=Area ))+geom_jitter(aes(x=Area, y=HYDROCm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROCm (minutes)")+xlab("Area")+ggtitle("g. HYDROCm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the HYDROV boxplot
p23 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=HYDROV, fill=Area ))+geom_jitter(aes(x=Area, y=HYDROV,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("HYDROV (ha)")+xlab("Area")+ggtitle("h. HYDROV for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WET boxplot
p24 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=WET, fill=Area ))+geom_jitter(aes(x=Area, y=WET,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WET (minutes)")+xlab("Area")+ggtitle("h. WET for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WETm boxplot
p25 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=WETm, fill=Area ))+geom_jitter(aes(x=Area, y=WETm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WETm (minutes)")+xlab("Area")+ggtitle("i. WETm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WETv boxplot
p26 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=WETv, fill=Area ))+geom_jitter(aes(x=Area, y=WETv,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WETv (ha)")+xlab("Area")+ggtitle("i. WETv for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLE boxplot
p27 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=GEOLE, fill=Area ))+geom_jitter(aes(x=Area, y=GEOLE,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLE (m.)")+xlab("Area")+ggtitle("a. GEOLE for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLEm boxplot
p28 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=GEOLEm, fill=Area ))+geom_jitter(aes(x=Area, y=GEOLEm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLEm (m.)")+xlab("Area")+ggtitle("b. GEOLEm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLC boxplot
p29 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=GEOLC, fill=Area ))+geom_jitter(aes(x=Area, y=GEOLC,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLC (minutes)")+xlab("Area")+ggtitle("c. GEOLC for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLCm boxplot
p30 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=GEOLCm, fill=Area ))+geom_jitter(aes(x=Area, y=GEOLCm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLCm (minutes)")+xlab("Area")+ggtitle("d. GEOLCm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the GEOLV boxplot
p31 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=GEOLV, fill=Area ))+geom_jitter(aes(x=Area, y=GEOLV,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("GEOLV (ha)")+xlab("Area")+ggtitle("a. GEOLV for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the CPFPCGs boxplot
p32 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=CPFPCGs, fill=Area ))+geom_jitter(aes(x=Area, y=CPFPCGs,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("CPFPCGs (ha)")+xlab("Area")+ggtitle("b. CPFPCGs for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the CPFPCDs boxplot
p33 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=CPFPCDs, fill=Area ))+geom_jitter(aes(x=Area, y=CPFPCDs,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("CPFPCDs (ha)")+xlab("Area")+ggtitle("c. CPFPCDs for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the CPFPCGc boxplot
p34 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=CPFPCGc, fill=Area ))+geom_jitter(aes(x=Area, y=CPFPCGc,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("CPFPCGc (minutes)")+xlab("Area")+ggtitle("e. CPFPCGc for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the CPFPCDc boxplot
p35 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=CPFPCDc, fill=Area ))+geom_jitter(aes(x=Area, y=CPFPCDc,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("CPFPCDc (minutes)")+xlab("Area")+ggtitle("f. CPFPCDc for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the VISC boxplot
p36 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=VISC, fill=Area ))+geom_jitter(aes(x=Area, y=VISC,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("VISC (ha)")+xlab("Area")+ggtitle("d. VISC for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the VISZ boxplot
p37 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=VISZ, fill=Area ))+geom_jitter(aes(x=Area, y=VISZ,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("VISZ (ha)")+xlab("Area")+ggtitle("e. VISZ for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the VISPR boxplot
p38 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=VISPR, fill=Area ))+geom_jitter(aes(x=Area, y=VISPR,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("VISPR")+xlab("Area")+ggtitle("g. VISPR for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the VISPRm boxplot
p39 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=VISPRm, fill=Area ))+geom_jitter(aes(x=Area, y=VISPRm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("VISPRm")+xlab("Area")+ggtitle("h. VISPRm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the LCPC boxplot
p40 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=LCPC, fill=Area ))+geom_jitter(aes(x=Area, y=LCPC,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("LCPC (minutes)")+xlab("Area")+ggtitle("i. LCPC for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the LCPCm boxplot
p41 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=LCPCm, fill=Area ))+geom_jitter(aes(x=Area, y=LCPCm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("LCPCm (minutes)")+xlab("Area")+ggtitle("a. LCPCm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TOTINS boxplot
p42 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=TOTINS, fill=Area ))+geom_jitter(aes(x=Area, y=TOTINS,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TOTINS")+xlab("Area")+ggtitle("b. TOTINS for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the TOTINSm boxplot
p43 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=TOTINSm, fill=Area ))+geom_jitter(aes(x=Area, y=TOTINSm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("TOTINSm")+xlab("Area")+ggtitle("c. TOTINSm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the DIRINS boxplot
p44 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=DIRINS, fill=Area ))+geom_jitter(aes(x=Area, y=DIRINS,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIRINS")+xlab("Area")+ggtitle("d. DIRINS for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the DIRINSm boxplot
p45 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=DIRINSm, fill=Area ))+geom_jitter(aes(x=Area, y=DIRINSm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIRINSm")+xlab("Area")+ggtitle("e. DIRINSm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the DIFINS boxplot
p46 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=DIFINS, fill=Area ))+geom_jitter(aes(x=Area, y=DIFINS,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIFINS")+xlab("Area")+ggtitle("f. DIFINS for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the DIFINSm boxplot
p47 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=DIFINSm, fill=Area ))+geom_jitter(aes(x=Area, y=DIFINSm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("DIFINSm")+xlab("Area")+ggtitle("g. DIFINSm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WIND boxplot
p48 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=WIND, fill=Area ))+geom_jitter(aes(x=Area, y=WIND,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WIND")+xlab("Area")+ggtitle("h. WIND for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  

## Create the WINDm boxplot
p49 <- ggplot(data = boxplot_northern_vs_central,col=c(123,234))+geom_boxplot(aes(x=Area, y=WINDm, fill=Area ))+geom_jitter(aes(x=Area, y=WINDm,fill=Area),alpha=0.6)+scale_fill_brewer(palette="PuBu")+ylab("WINDm")+xlab("Area")+ggtitle("i. WINDm for the sites of each area")+ theme(plot.title = element_text(hjust = 0.5))+ theme(legend.position = "none")  
```

## Create Figures 14 and 15

```{r echo=TRUE, results='hide'}
## create Figure 14 
(p8 | p9 | p12) /
  (p13 | p14 | p15) /
  (p16 | p23 | p26)


png(file = "~/output/Figure14.png",width = 1506,height = 750)


## create Figure 15 
(p31 | p32 | p33) /
  (p36 | p37 | guide_area())

png(file = "~/output/Figure15.png",width = 1506,height = 600)
```

## Create Suplementary Material figures

```{r echo=TRUE, results='hide'}
## create Figure 15 SM
(p | p1 | p2) /
  (p3 | p4 | p5) /
  (p6 | p7 | p10)

png(file = "~/output/Figure15-SM.png",width = 1506,height = 750)

## create Figure 16 SM
(p11 | p17 | p18) /
  (p19 | p20 | p21) /
  (p22 | p24| p25)

png(file = "~/otuput/Figure16-SM.png",width = 1506,height = 750)

## create Figure 17 SM
(p27 | p28 | p29) /
  (p30 | p34 | p35) /
  (p38 | p39 | p40)

png(file = "~/output/Figure17-SM.png",width = 1506,height = 750)

## create Figure 18 SM
(p41 | p42 | p43) /
  (p44 | p45 | p46) /
  (p47 | p48| p49)

png(file = "~/output/Figure18-SM.png",width = 1506,height = 750)
```

# Statistical tests
XXX

## Northern area

```{r echo=TRUE, results='hide'}
## Import files
test_northern <- read.csv(file = "~/csv/boxplot_variables_northern.csv",header=TRUE, sep=";", stringsAsFactors=F, dec=",")

## Install and load Rcmdr package
install.packages("Rcmdr")
library(Rcmdr)

# ALTm
## Shapiro-Wilk Test to check Normality 
normalityTest(~ALTm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(ALTm ~ Type, alternative="two.sided", data=test_northern) # Shows different variances p-value < 0.05 -- T Welch test#

## T Welch Test for independent samples
t.test(ALTm~Type, alternative='two.sided', conf.level=.95, var.equal=FALSE, # Shows different variances p-value < 0.05 -- Samples from different populations#
       data=test_northern)

# TPI100m
## Normality Test
normalityTest(~TPI100m, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(TPI100m ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(TPI100m~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from different populations#
       data=test_northern)


# TPI500m
## Normality Test
normalityTest(~TPI500m, test="shapiro.test", data=test_northern) # Shows normality p-value > 0.05 -- F test#

## F Test for check parametric homoscedasticity/variances (medians by group)
var.test(TPI500m ~ Type, alternative='two.sided', conf.level=.95, 
         data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(TPI500m~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# TPI1000m
## Normality Test
normalityTest(~TPI1000m, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(TPI1000m ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(TPI1000m~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# SLOm
## Shapiro-Wilk Test to check Normality 
normalityTest(~SLOm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(SLOm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(SLOm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# ASPm
## Shapiro-Wilk Test to check Normality 
normalityTest(~ASPm, test="shapiro.test", data=test_northern) # Shows normality p-value > 0.05 -- F test#

## F Test for check parametric homoscedasticity/variances (medians by group)
var.test(ASPm ~ Type, alternative='two.sided', conf.level=.95, 
         data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(ASPm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# HYDROEm
## Shapiro-Wilk Test to check Normality 
normalityTest(~HYDROEm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(HYDROEm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(HYDROEm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# HYDROCm
## Shapiro-Wilk Test to check Normality 
normalityTest(~HYDROCm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(HYDROCm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(HYDROCm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# WETm
## Shapiro-Wilk Test to check Normality 
normalityTest(~WETm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(WETm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T student test#

## T Student Test for independent samples
t.test(WETm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# GEOLEm
## Shapiro-Wilk Test to check Normality 
normalityTest(~GEOLEm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(GEOLEm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value < 0.05 -- T Welch test#

## T Welch Test for independent samples
t.test(GEOLEm~Type, alternative='two.sided', conf.level=.95, var.equal=FALSE, # Shows different variances p-value < 0.05 -- Samples from different populations#
       data=test_northern)


# GEOLCm
## Shapiro-Wilk Test to check Normality 
normalityTest(~GEOLCm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(GEOLCm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value < 0.05 -- T Welch test#

## T Welch Test for independent samples
t.test(GEOLCm~Type, alternative='two.sided', conf.level=.95, var.equal=FALSE, # Shows different variances p-value < 0.05 -- Samples from different populations#
       data=test_northern)


# VISPRm
## Shapiro-Wilk Test to check Normality 
normalityTest(~VISPRm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(VISPRm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T Student test#

## T Student Test for independent samples
t.test(VISPRm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# LCPCm
## Shapiro-Wilk Test to check Normality 
normalityTest(~LCPCm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(LCPCm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T Student test#

## T Student Test for independent samples
t.test(LCPCm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# TOTINSm
## Shapiro-Wilk Test to check Normality 
normalityTest(~TOTINSm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(TOTINSm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T Student test#

## T Student Test for independent samples
t.test(TOTINSm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# DIRINSm
## Shapiro-Wilk Test to check Normality 
normalityTest(~DIRINSm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(DIRINSm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T Student test#

## T Student Test for independent samples
t.test(DIRINSm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)


# DIFINSm
## Shapiro-Wilk Test to check Normality 
normalityTest(~DIFINSm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(DIFINSm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value < 0.05 -- T Welch test#

## T Welch Test for independent samples
t.test(DIFINSm~Type, alternative='two.sided', conf.level=.95, var.equal=FALSE, # Shows different variances p-value < 0.05 -- Samples from different populations#
       data=test_northern)


# WINDm
## Shapiro-Wilk Test to check Normality 
normalityTest(~WINDm, test="shapiro.test", data=test_northern) # Shows non normality p-value < 0.05 -- Wilcoxon test#

## Wilcoxon Test for check non parametric homoscedasticity/variances (medians by group)
wilcox.test(WINDm ~ Type, alternative="two.sided", data=test_northern) # Shows same variance p-value > 0.05 -- T Student test#

## T Student Test for independent samples
t.test(WINDm~Type, alternative='two.sided', conf.level=.95, var.equal=TRUE, # p-value > 0.05 -- Samples from same population#
       data=test_northern)
```