---
title: "TBC *"
author: "Mikel Diaz-Rodriguez"
date: "March 7th, 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE,
                      echo = TRUE)
```

# Introduction

This document contains code to enable reproducibility of the paper "Living in the mountains. Settlement patterns in Northwestern Iberia during Palaeolithic period".

For this, it is necessary to execute the steps shown in the following lines.

# Complete Spatial Randomness

### Necessary packages

Import the necessary packages to analyse the CSR.

```{r echo=FALSE, results='hide'}
# ipak function: install and load multiple R packages.
# check to see if packages are installed. Install them if they are not, then load them into the R session.

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
# usage
packages <- c("GGally", "readxl", "rgdal", "rgeos", "sp", "spatstat", "tidyverse", "dismo", "MASS", "ggplot2", "plyr", "maps", "maptools", "raster", "geostatsp", "patchwork", "foreach", "purrrlyr")
ipak(packages)
```

### Import data

Import the data used in CSR analysis.

```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
# set your working directory
setwd("~/mountain_ranges/shp")

# add the study areas
area_northern <- readOGR(dsn="area_northern.shp", layer="area_northern")
area_central <- readOGR(dsn="area_central.shp", layer="area_central")

# and check it
plot(area_northern)
plot(area_central)

# add the sites
sites_northern <- readOGR(dsn="sites_northern.shp", layer="sites_northern")
sites_central <- readOGR(dsn="sites_central.shp", layer="sites_central")

# add the random sites
random_sites_northern <- readOGR(dsn="random_sites_northern.shp", layer="random_sites_northern")
random_sites_central <- readOGR(dsn="random_sites_central.shp", layer="random_sites_central")

# plot each study area, sites and the random sites and check if everything looks OK
## check the Northern Mountain range area
plot(area_northern)
plot(sites_northern, col="blue", pch=20, add=T)
plot(random_sites_northern, col="grey", pch=20, add=T)

## check the Central Mountain range area
plot(area_central)
plot(sites_central, col="red", pch=20, add=T)
plot(random_sites_central, col="grey", pch=20, add=T)

# remove any sites with the same grid reference
sites_northern <- remove.duplicates(sites_northern)
sites_central <- remove.duplicates(sites_central)

# select the points inside each study area 
sitesSubN <- sites_northern[area_northern,]
sitesSubC <- sites_central[area_central,]



# check to see that the points have been removed in each area
## Northern Mountain ranges
plot(area_northern)
plot(sitesSubN, col="red", pch=20, add=T)

## Central Mountain ranges
plot(area_central)
plot(sitesSubC, col="red", pch=20, add=T)


# set a window as the Northern area
window1 <- as.owin(area_northern)
plot(window1)

# create a ppp object
sitesSubN.ppp <- ppp(x=sitesSubN$utmx,y=sitesSubN$utmy,window=window1)

# plot the sites and the Northern area
plot(sitesSubN.ppp,pch=16,cex=0.5, main="Northern Mountain range sites")


# set a window as the Central area
window2 <- as.owin(area_central)
plot(window2)

# create a ppp object
sitesSubC.ppp <- ppp(x=sitesSubC$utmx,y=sitesSubC$utmy,window=window2)

# plot the sites and the Northern area
plot(sitesSubC.ppp,pch=16,cex=0.5, main="Central Mountain range sites")
```

### Check the CSR

```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
# CSR Analysis

## Northern Mountain ranges
### Normality test for sites
shapiro.test(sitesSubN$utmx)

### Normality test for random sites
shapiro.test(random_sites_northern$utmx)

### If the alternative hypothesis is accepted, the points do not follow a normal distribution. To verify this, the K-S Test is used.
### K-S is a non-parametric test to check if the points of both samples belong to the same population.
ks.test(sitesSubN$utmx,random_sites_northern$utmx)


## Central Mountain ranges
### Normality test for sites
shapiro.test(sitesSubC$utmx)

### Normality test for random sites
shapiro.test(random_sites_central$utmx)

### K-S Test
ks.test(sitesSubC$utmx,random_sites_central$utmx)
```

### Create Figures 2 and 3

```{r echo=TRUE, results='hide'}
## K, L and G Functions
# set the simulations
sims <- 99
# to get 95% envelope
nrank <- round((sims + 1) / 100 * 2.5, 0)

# K, L and G functions for Northern Mountain ranges
KfunctionN <- envelope(sitesSubN.ppp,Kest, nsim=sims,rank=nrank, correction="best") 
KinhomFunctionN <- envelope(sitesSubN.ppp,Kinhom, nsim=sims,rank=nrank, correction="best")
LFunctionN <- envelope(sitesSubN.ppp,Lest, nsim=sims,rank=nrank, correction="best")
LinhomFunctionN <- envelope(sitesSubN.ppp,Linhom, nsim=sims,rank=nrank, correction="best")
GFunctionN <- envelope(sitesSubN.ppp,Gest, nsim=sims,rank=nrank, correction="best")
GinhomFunctionN <- envelope(sitesSubN.ppp,Ginhom, nsim=sims,rank=nrank, correction="best")

# K, L and G functions for Central Mountain ranges
KfunctionC <- envelope(sitesSubC.ppp,Kest, nsim=sims,rank=nrank, correction="best") 
KinhomFunctionC <- envelope(sitesSubC.ppp,Kinhom, nsim=sims,rank=nrank, correction="best")
LFunctionC <- envelope(sitesSubC.ppp,Lest, nsim=sims,rank=nrank, correction="best")
LinhomFunctionC <- envelope(sitesSubC.ppp,Linhom, nsim=sims,rank=nrank, correction="best")
GFunctionC <- envelope(sitesSubC.ppp,Gest, nsim=sims,rank=nrank, correction="best")
GinhomFunctionC <- envelope(sitesSubC.ppp,Ginhom, nsim=sims,rank=nrank, correction="best")

# create Figure 2
par(mar=c(3, 3, 3, 3), mfrow=c(3,2))
plot(KfunctionN,main="a. K Function for the Northern area (homogeneous)",legend=FALSE)
plot(KinhomFunctionN,main="b. K Function for the Northern area (inhomogeneous)",legend=FALSE)
plot(LFunctionN,main="c. L Function for the Northern area (homogeneous)",legend=FALSE)
plot(LinhomFunctionN,main="d. L Function for the Northern area (inhomogeneous)",legend=FALSE) 
plot(GFunctionN,main="e. G Function for the Northern area (homogeneous)",legend=FALSE) 
plot(GinhomFunctionN,main="f. G Function for the Northern area (inhomogeneous)",legend=FALSE)
par(mfrow=c(1,1))
png(file = "~/output/Figure2.png",width = 900,height = 1200)
dev.off()

# create Figure 3
par(mar=c(3, 3, 3, 3), mfrow=c(3,2))
plot(KfunctionC,main="a. K Function for the Central area (homogeneous)",legend=FALSE)
plot(KinhomFunctionC,main="b. K Function for the Central area (inhomogeneous)",legend=FALSE)
plot(LFunctionC,main="c. L Function for the Central area (homogeneous)",legend=FALSE)
plot(LinhomFunctionC,main="d. L Function for the Central area (inhomogeneous)",legend=FALSE) 
plot(GFunctionC,main="e. G Function for the Central area (homogeneous)",legend=FALSE) 
plot(GinhomFunctionC,main="f. G Function for the Central area (inhomogeneous)",legend=FALSE)
par(mfrow=c(1,1))
png(file = "~/output/Figure3.png",width = 900,height = 1200)
dev.off()
```

### Kernel density plots

Process to create the kernel density plots comparing archaeological sites and 999 randomly resampled background points.

```{r echo=TRUE, results='hide'}
# Northern area

## set your working directory
setwd("~/mountain_ranges/shp")

## add the sites
sites_northern <- readOGR(dsn="sites_northern.shp", layer="sites_northern")


## set the working directory
setwd("~/mountain_ranges/grids")

## Import variables and set the same extent for everyone

ALTA_northern <- raster("ALTA_northern.tif")

TPI100_northern <- raster("TPI100_northern.asc")

TPI500_northern <- raster("TPI500_northern.asc")

TPI1000_northern <- raster("TPI1000_northern.asc")

SLO_northern <- raster("SLO_northern.tif") 

ASP_northern <- raster("ASP_northern.tif") 

HYDROE_northern <- raster("HYDROE_northern.tif")

HYDROC_northern <- raster("HYDROC_northern.tif") 

WET_northern <- raster("WET_northern.tif") 

GEOLE_northern <- raster("GEOLE_northern.tif")

GEOLC_northern <- raster("GEOLC_northern.tif")

VISPR_northern <- raster("VISPR_northern.tif")

LCPC_northern <- raster("LCPC_northern.tif")

TOTINS_northern <- raster("TOTINS_northern.asc") 

DIRINS_northern <- raster("DIRINS_northern.asc") 

DIFINS_northern <- raster("DIFINS_northern.asc")  

WIND_northern <- raster("WIND_northern.asc") 

CPFPCGc_northern <- raster("CPFPCGc_northern.tif")

CPFPCDc_northern <- raster("CPFPCDc_northern.tif")
```

## ALTA

Create kernel density plot graph for the variable ALTA.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`ALTA (m)` <-  
  raster::extract(ALTA_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  ALTA_northern %>%
  density(from = 450, to = 766, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(ALTA = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_ALTA_values <- ALTA_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_ALTA_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_ALTA_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 53, to = 1054, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("ALTA", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_ALTA_densities,
            mapping = aes(x = ALTA,
                          y = Frequency)) +
  geom_ribbon(data = background_ALTA_densities,
              mapping = aes(x = ALTA,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = ALTA ,
                          y = Frequency),
            color = "red") +ggtitle("a. ALTA in Northern Mountain ranges")



# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_altitude_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_ALTA_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`ALTA (m)`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_altitude_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_altitude_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_altitude_MWU, 3)
```

## TPI100

Create kernel density plot graph for the variable TPI100.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TPI100` <-  
  raster::extract(TPI100_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TPI100_northern %>%
  density(from = -3, to = 10, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TPI100 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI100_values <- TPI100_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI100_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI100_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = -34, to = 30, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI100", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI100_densities,
            mapping = aes(x = TPI100,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI100_densities,
              mapping = aes(x = TPI100,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TPI100,
                          y = Frequency),
            color = "red") +ggtitle("b. TPI100 in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI100_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI100_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TPI100`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI100_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI100_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI100_MWU, 3)
```

##TPI500

Create kernel density plot graph for the variable TPI500.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TPI500` <-  
  raster::extract(TPI500_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TPI500_northern %>%
  density(from = -3, to = 10.5, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TPI500 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI500_values <- TPI500_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI500_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI500_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = -106, to = 114, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI500", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI500_densities,
            mapping = aes(x = TPI500,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI500_densities,
              mapping = aes(x = TPI500,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TPI500,
                          y = Frequency),
            color = "red") +ggtitle("a. TPI500 variable in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI500_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI500_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TPI500`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI500_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI500_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI500_MWU, 3)
```

##TPI1000

Create kernel density plot graph for the variable TPI1000.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TPI1000` <-  
  raster::extract(TPI1000_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TPI1000_northern %>%
  density(from = -3, to = 10, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TPI1000 = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TPI1000_values <- TPI1000_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TPI1000_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TPI1000_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = -163, to = 205, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TPI1000", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TPI1000_densities,
            mapping = aes(x = TPI1000,
                          y = Frequency)) +
  geom_ribbon(data = background_TPI1000_densities,
              mapping = aes(x = TPI1000,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TPI1000,
                          y = Frequency),
            color = "red") +ggtitle("b. TPI1000 in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TPI1000_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TPI1000_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TPI1000`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TPI1000_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TPI1000_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TPI1000_MWU, 3)
```

##SLO

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`SLO` <-  
  raster::extract(SLO_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  SLO_northern %>%
  density(from = 0, to = 26, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(SLO = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_SLO_values <- SLO_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_SLO_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_SLO_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 61, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("SLO", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_SLO_densities,
            mapping = aes(x = SLO,
                          y = Frequency)) +
  geom_ribbon(data = background_SLO_densities,
              mapping = aes(x = SLO,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = SLO,
                          y = Frequency),
            color = "red") +ggtitle("c. SLO in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_SLO_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_SLO_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`SLO`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_SLO_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_SLO_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_SLO_MWU, 3)
```

##ASP

Create kernel density plot graph for the variable ASP.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`ASP` <-  
  raster::extract(ASP_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  ASP_northern %>%
  density(from = 11, to = 331, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(ASP = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_ASP_values <- ASP_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_ASP_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_ASP_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 360, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("ASP", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_ASP_densities,
            mapping = aes(x = ASP,
                          y = Frequency)) +
  geom_ribbon(data = background_ASP_densities,
              mapping = aes(x = ASP,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = ASP,
                          y = Frequency),
            color = "red") +ggtitle("c. ASP in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_ASP_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_ASP_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`ASP`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_ASP_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_ASP_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_ASP_MWU, 3)
```

##HYDROE

Create kernel density plot graph for the variable HYDROE.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`HYDROE` <-  
  raster::extract(HYDROE_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())

## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  HYDROE_northern %>%
  density(from = 34, to = 1784, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(HYDROE = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_HYDROE_values <- HYDROE_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_HYDROE_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_HYDROE_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 2834, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("HYDROE", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_HYDROE_densities,
            mapping = aes(x = HYDROE,
                          y = Frequency)) +
  geom_ribbon(data = background_HYDROE_densities,
              mapping = aes(x = HYDROE,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = HYDROE,
                          y = Frequency),
            color = "red") +ggtitle("d. HYDROE in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_HYDROE_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_HYDROE_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`HYDROE`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_HYDROE_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_HYDROE_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_HYDROE_MWU, 3)
```

##HYDROC

Create kernel density plot graph for the variable HYDROC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`HYDROC` <-  
  raster::extract(HYDROC_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  HYDROC_northern %>%
  density(from = 3, to = 100, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(HYDROC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_HYDROC_values <- HYDROC_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_HYDROC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_HYDROC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 144, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("HYDROC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_HYDROC_densities,
            mapping = aes(x = HYDROC,
                          y = Frequency)) +
  geom_ribbon(data = background_HYDROC_densities,
              mapping = aes(x = HYDROC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = HYDROC,
                          y = Frequency),
            color = "red") +ggtitle("d. HYDROC in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_HYDROC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_HYDROC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`HYDROC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_HYDROC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_HYDROC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_HYDROC_MWU, 3)
```

##WET

Create kernel density plot graph for the variable WET.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WET` <-  
  raster::extract(WET_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WET_northern %>%
  density(from = 0, to = 45, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WET = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WET_values <- WET_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WET_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 113, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WET", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WET_densities,
            mapping = aes(x = WET,
                          y = Frequency)) +
  geom_ribbon(data = background_WET_densities,
              mapping = aes(x = WET,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WET,
                          y = Frequency),
            color = "red") +ggtitle("a. WET in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WET_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WET`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WET_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WET_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WET_MWU, 3)
```

##GEOLE

Create kernel density plot graph for the variable GEOLE.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WET` <-  
  raster::extract(WET_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WET_northern %>%
  density(from = 0, to = 45, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WET = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WET_values <- WET_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WET_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 113, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WET", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WET_densities,
            mapping = aes(x = WET,
                          y = Frequency)) +
  geom_ribbon(data = background_WET_densities,
              mapping = aes(x = WET,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WET,
                          y = Frequency),
            color = "red") +ggtitle("a. WET in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WET_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WET_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WET`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WET_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WET_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WET_MWU, 3)
```

##GEOLC

Create kernel density plot graph for the variable GEOLC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`GEOLC` <-  
  raster::extract(GEOLC_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  GEOLC_northern %>%
  density(from = 0, to = 153, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(GEOLC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_GEOLC_values <- GEOLC_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_GEOLC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_GEOLC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 360, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("GEOLC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_GEOLC_densities,
            mapping = aes(x = GEOLC,
                          y = Frequency)) +
  geom_ribbon(data = background_GEOLC_densities,
              mapping = aes(x = GEOLC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = GEOLC,
                          y = Frequency),
            color = "red") +ggtitle("c. GEOLC in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_GEOLC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_GEOLC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`GEOLC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_GEOLC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_GEOLC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_GEOLC_MWU, 3)
```

##VISPR

Create kernel density plot graph for the variable VISPR.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`VISPR` <-  
  raster::extract(VISPR_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  VISPR_northern %>%
  density(from = 0, to = 75, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(VISPR = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_VISPR_values <- VISPR_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_VISPR_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_VISPR_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 153, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("VISPR", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_VISPR_densities,
            mapping = aes(x = VISPR,
                          y = Frequency)) +
  geom_ribbon(data = background_VISPR_densities,
              mapping = aes(x = VISPR,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = VISPR,
                          y = Frequency),
            color = "red") +ggtitle("d. VISPR in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_VISPR_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_VISPR_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`VISPR`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_VISPR_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_VISPR_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_VISPR_MWU, 3)
```

##LCPC

Create kernel density plot graph for the variable LCPC.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`LCPC` <-  
  raster::extract(LCPC_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  LCPC_northern %>%
  density(from = 0, to = 9.95, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(LCPC = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_LCPC_values <- LCPC_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_LCPC_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_LCPC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 142, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("LCPC", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_LCPC_densities,
            mapping = aes(x = LCPC,
                          y = Frequency)) +
  geom_ribbon(data = background_LCPC_densities,
              mapping = aes(x = LCPC,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = LCPC,
                          y = Frequency),
            color = "red") +ggtitle("a. LCPC in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_LCPC_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_LCPC_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`LCPC`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_LCPC_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_LCPC_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_LCPC_MWU, 3)
```

##TOTINS

Create kernel density plot graph for the variable TOTINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`TOTINS` <-  
  raster::extract(TOTINS_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  TOTINS_northern %>%
  density(from = 3.5, to = 5.2, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(TOTINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_TOTINS_values <- TOTINS_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_TOTINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_TOTINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0.7, to = 6.37, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("TOTINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_TOTINS_densities,
            mapping = aes(x = TOTINS,
                          y = Frequency)) +
  geom_ribbon(data = background_TOTINS_densities,
              mapping = aes(x = TOTINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = TOTINS,
                          y = Frequency),
            color = "red") +ggtitle("a. TOTINS in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_TOTINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_TOTINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`TOTINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_TOTINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_TOTINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_TOTINS_MWU, 3)
```

##DIRINS

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`DIRINS` <-  
  raster::extract(DIRINS_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  DIRINS_northern %>%
  density(from = 2.6, to = 4.5, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(DIRINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_DIRINS_values <- DIRINS_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_DIRINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_DIRINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 5.6, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("DIRINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_DIRINS_densities,
            mapping = aes(x = DIRINS,
                          y = Frequency)) +
  geom_ribbon(data = background_DIRINS_densities,
              mapping = aes(x = DIRINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = DIRINS,
                          y = Frequency),
            color = "red") +ggtitle("b. DIRINS in Northern Mountain ranges")




# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_DIRINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_DIRINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`DIRINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_DIRINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_DIRINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_DIRINS_MWU, 3)
```

##DIFINS

Create kernel density plot graph for the variable DIFINS.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`DIFINS` <-  
  raster::extract(DIFINS_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  DIFINS_northern %>%
  density(from = 0.8, to = 0.93, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(DIFINS = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_DIFINS_values <- DIFINS_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_DIFINS_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_DIFINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0.69, to = 0.98, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("DIFINS", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_DIFINS_densities,
            mapping = aes(x = DIFINS,
                          y = Frequency)) +
  geom_ribbon(data = background_DIFINS_densities,
              mapping = aes(x = DIFINS,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = DIFINS,
                          y = Frequency),
            color = "red") +ggtitle("c. DIFINS in Northern Mountain ranges")





# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_DIFINS_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_DIFINS_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`DIFINS`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_DIFINS_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_DIFINS_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_DIFINS_MWU, 3)
```

##WIND

Create kernel density plot graph for the variable SLO.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`WIND` <-  
  raster::extract(WIND_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  WIND_northern %>%
  density(from = 0.7, to = 1.24, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(WIND = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_WIND_values <- WIND_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_WIND_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_WIND_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0.74, to = 1.34, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("WIND", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_WIND_densities,
            mapping = aes(x = WIND,
                          y = Frequency)) +
  geom_ribbon(data = background_WIND_densities,
              mapping = aes(x = WIND,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = WIND,
                          y = Frequency),
            color = "red") +ggtitle("b. WIND variable in Northern Mountain ranges")



# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_WIND_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_WIND_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`WIND`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_WIND_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_WIND_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_WIND_MWU, 3)
```

##CPFPCGc

Create kernel density plot graph for the variable CPFPCGc.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`CPFPCGc` <-  
  raster::extract(CPFPCGc_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  CPFPCGc_northern %>%
  density(from = 4, to = 432, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(CPFPCGc = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_CPFPCGc_values <- CPFPCGc_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_CPFPCGc_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_CPFPCGc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 673, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("CPFPCGc", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_CPFPCGc_densities,
            mapping = aes(x = CPFPCGc,
                          y = Frequency)) +
  geom_ribbon(data = background_CPFPCGc_densities,
              mapping = aes(x = CPFPCGc,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = CPFPCGc ,
                          y = Frequency),
            color = "red") +ggtitle("c. CPFPCGc in Northern Mountain ranges")



# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_CPFPCGc_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_CPFPCGc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`CPFPCGc`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_CPFPCGc_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_CPFPCGc_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_CPFPCGc_MWU, 3)
```

##CPFPCDc

Create kernel density plot graph for the variable CPFPCDc.

```{r echo=TRUE, results='hide'}
## Extract cell site from the Northern area
sites_northern_spdf <- SpatialPointsDataFrame(sites_northern, data.frame(sites_northern))


sites_northern$`CPFPCDc` <-  
  raster::extract(CPFPCDc_northern, 
                  sites_northern_spdf)

## Delete the grey theme
theme_set(theme_bw())


## Calculate the sites densities for Central area
sites_northern_densities <- sites_northern %$%
  CPFPCDc_northern %>%
  density(from = 0, to = 0, n = 34) %>%
  broom::tidy() %>%
  tibble::as_tibble() %>%
  dplyr::mutate(y = y * 34) %>%
  dplyr::rename(CPFPCDc = x,
                Frequency = y)

## Calculate possible densities across the study area using resampling
background_CPFPCDc_values <- CPFPCDc_northern %>%
  values() %>%
  na.omit() # Drop all masked (NA) locations

# Draw 999 random samples, and calculate their densities
background_CPFPCDc_densities <- foreach::foreach(n = 1:999, .combine = rbind) %do% {
  background_CPFPCDc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    density(from = 0, to = 8.7, n = 34) %>%
    broom::tidy() %>%
    tibble::as_tibble() %>%
    dplyr::mutate(y = y * 34)
} %>%
  dplyr::group_by(x) %>%
  purrrlyr::by_slice(function(x){
    quantile(x$y, probs = c(0.025, 0.5, 0.975)) %>%
      t() %>%
      broom::tidy()
  }, .collate = "cols") %>%
  magrittr::set_names(c("CPFPCDc", "Lower CI", "Frequency", "Upper CI"))

# Plot distributions
ggplot() +
  geom_line(data = background_CPFPCDc_densities,
            mapping = aes(x = CPFPCDc,
                          y = Frequency)) +
  geom_ribbon(data = background_CPFPCDc_densities,
              mapping = aes(x = CPFPCDc,
                            ymin = `Lower CI`,
                            ymax = `Upper CI`),
              alpha = 0.3) +
  geom_line(data = sites_northern_densities,
            mapping = aes(x = CPFPCDc ,
                          y = Frequency),
            color = "red") +ggtitle("d. CPFPCDc in Northern Mountain ranges")



# Draw 999 random samples from background, and compute two-sample Wilcoxon tests (Mann-Whitney U tests)
background_CPFPCDc_MWU <- foreach(n = 1:999, .combine = rbind) %do% {
  background_sample <- background_CPFPCDc_values %>%
    sample(nrow(sites_northern),
           replace = FALSE) %>%
    wilcox.test(x = sites_northern$`CPFPCGc`,
                y = .,
                alternative = "greater",
                exact = FALSE) %>%
    broom::tidy() %>%
    tibble::as_tibble()
  
} %>%
  dplyr::select(statistic, p.value)


# Get the median test statistic and 95% confidence interval
background_CPFPCDc_MWU <- foreach::foreach(prob = c(0.025,0.5,0.975), .combine = rbind) %do% {
  background_CPFPCDc_MWU %>%
    dplyr::summarise_all(quantile, probs = prob)
} %>%
  t() %>%
  magrittr::set_colnames(c("Lower CI","Median","Upper CI")) %>%
  magrittr::set_rownames(c("U statistic","p-value"))



round(background_CPFPCDc_MWU, 3)
```

# Crear graficos de barras

### Paquetes necesarios

Importacion de los paquetes necesarios para crear los graficos de barras.

```{r echo=TRUE, results='hide'}
spatpack<-c("spatstat","dismo", "MASS", "ggplot2", "plyr", "sp","maps","maptools","raster","geostatsp","rgdal")
lapply(spatpack, require, character.only = TRUE)
```

### Importar Datos

Paso consistente en importar los datos de los csv.

```{r, message=FALSE, warning=FALSE, paged.print=FALSE}
altplot <- read.table(file="csv/altplot.csv",header=TRUE, sep=";")
altplot1 <- read.table(file="csv/altplot1.csv",header=TRUE, sep=";")
altplot2 <- read.table(file="csv/altplot2.csv",header=TRUE, sep=";")
altplot3 <- read.table(file="csv/altplot3.csv",header=TRUE, sep=";")
altplot4 <- read.table(file="csv/altplot4.csv",header=TRUE, sep=";")
```

### Crear Figura 2A

Crear y exportar grafico de barras relativo a la altitud.

```{r echo=TRUE, results='hide'}
altplot$Altitud <- factor (altplot$Altitud, levels = c("0-100", "100-200","200-300","300-400","400-500","500-600","600-700","700-800","800-900","900-1000","1000-1100","1100-1200","1200-1300","1300-1400","1400-1500"))  

p <- ggplot(altplot,aes(Altitud,Porcentaje)) + geom_bar(data=subset(altplot,Categoria=="Terreno"),stat="identity", fill="gray") + geom_line(data=subset(altplot,Categoria=="Yacimiento"), aes(group="Categoria", colour="red"),size=1.5) + guides(colour=FALSE) + theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold")) + labs(title = "", y = "Porcentaje", x = "Altitud (msnm)")  
p <- p + theme( 
  panel.background = element_rect(fill = "transparent",colour = NA), 
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank(), 
  plot.background = element_rect(fill = "transparent",colour = NA) 
)
plot(p)

pdf(file = "~output/Figura2A.pdf",width = 5,height = 12)
```

### Crear Figura 2B

Crear y exportar grafico de barras relativo a la pendiente.

```{r echo=TRUE, results='hide'}
altplot1$Pendiente <- factor (altplot1$Pendiente, levels = c("0-5", "5-10","10-15","15-20","20-25","25-30","30-35","35-40","40-45","45-50","50-55","55-60","60-65"))  

p1 <- ggplot(altplot1,aes(Pendiente,Porcentaje)) + geom_bar(data=subset(altplot1,Categoria=="Terreno"),stat="identity", fill="gray") + geom_line(data=subset(altplot1,Categoria=="Yacimiento"), aes(group="Categoria", colour="red"),size=1.5) + guides(colour=FALSE) + theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold"))+ labs(title = "", y = "Porcentaje", x = "Pendiente (grados)")   
p1 <- p1 + theme( 
  panel.background = element_rect(fill = "transparent",colour = NA), 
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank(), 
  plot.background = element_rect(fill = "transparent",colour = NA) 
)
plot(p1)

pdf(file = "~output/Figura2B.pdf",width = 5,height = 12)
```

### Crear Figura 2C

Crear y exportar grafico de barras relativo al coste a la hidrologia potencial.

```{r echo=TRUE, results='hide'}
altplot2$Coste <- factor (altplot2$Coste, levels = c("0-1000", "1000-2000","2000-3000","3000-4000","4000-5000","5000-6000","6000-7000","7000-8000","8000-9000","9000-10000","10000-11000","11000-12000","12000-13000"))  

p2 <- ggplot(altplot2,aes(Coste,Porcentaje)) + geom_bar(data=subset(altplot2,Categoria=="Terreno"),stat="identity", fill="gray") + geom_line(data=subset(altplot2,Categoria=="Yacimiento"), aes(group="Categoria", colour="red"),size=1.5) + guides(colour=FALSE) + theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold"))+ labs(title = "", y = "Porcentaje", x = "Coste a hidrologia (segundos)")   
p2 <- p2 + theme( 
  panel.background = element_rect(fill = "transparent",colour = NA), 
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank(), 
  plot.background = element_rect(fill = "transparent",colour = NA) 
)
plot(p2)

pdf(file = "~output/Figura2C.pdf",width = 5,height = 12)
```

### Crear Figura 2D

Crear y exportar grafico de barras relativo al coste a las zonas de humedal.

```{r echo=TRUE, results='hide'}
altplot3$Coste <- factor (altplot3$Coste, levels = c("0-1000", "1000-2000","2000-3000","3000-4000","4000-5000","5000-6000","6000-7000","7000-8000","8000-9000","9000-10000","10000-11000","11000-12000"))  

p3 <- ggplot(altplot3,aes(Coste,Porcentaje)) + geom_bar(data=subset(altplot3,Categoria=="Terreno"),stat="identity", fill="gray") + geom_line(data=subset(altplot3,Categoria=="Yacimiento"), aes(group="Categoria", colour="red"),size=1.5) + guides(colour=FALSE) + theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold"))+ labs(title = "", y = "Porcentaje", x = "Coste a zonas de humedal (segundos)") 
p3 <- p3 + theme( 
  panel.background = element_rect(fill = "transparent",colour = NA), 
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank(), 
  plot.background = element_rect(fill = "transparent",colour = NA) 
)
plot(p3)

pdf(file = "~output/Figura2D.pdf",width = 5,height = 12)
```

### Crear Figura 2E

Crear y exportar grafico de barras relativo al indice de prominencia visual.

```{r echo=TRUE, results='hide'}
altplot4$Indice <- factor (altplot4$Indice, levels = c("0-20", "20-40","40-60","60-80","80-100","100-120","120-140","140-160","160-180","180-200"))  

p4 <- ggplot(altplot4,aes(Indice,Porcentaje)) + geom_bar(data=subset(altplot4,Categoria=="Terreno"),stat="identity", fill="gray") + geom_line(data=subset(altplot4,Categoria=="Yacimiento"), aes(group="Categoria", colour="red"),size=1.5) + guides(colour=FALSE) + theme(axis.text=element_text(size=12),axis.title=element_text(size=14,face="bold"))+ labs(title = "", y = "Porcentaje", x = "Indice de Prominencia Visual")  
p4 <- p4 + theme( 
  panel.background = element_rect(fill = "transparent",colour = NA), 
  panel.grid.minor = element_blank(), 
  panel.grid.major = element_blank(), 
  plot.background = element_rect(fill = "transparent",colour = NA) 
)
plot(p4)

pdf(file = "~output/Figura2E.pdf",width = 5,height = 12)
```
